% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=7in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Jack Blumenau}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
 
\begin{letter}{Department of Government \\
London School of Economics}


\begin{flushleft}
{\large\bf Jack Blumenau, PhD. Candidate, London School of Economics}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
\hfill 07742 506757, j.blumenau@lse.ac.uk, 29c Marquis Road, Finsbury Park, London, N4 3AN 
\end{flushright} 
 % forces letterhead to top of page

 \vfill
\opening{Dear Sir or Madam,} 
 
\noindent I would like to be considered for the class teacher positions for the coming year in the Department of Methodology. 
 
\noindent Over the past year I have taught extensively for the Methodology Department, teaching both introductory and advanced courses, for which I received extremely positive teaching evaluations. I developed strong relationships with both the students and my fellow teachers on these courses, and have continued to mentor a number of students in their MA theses. I thoroughly enjoyed this experience and would like to build on this by teaching on further courses this year. I would like to be considered for the following courses: MY452, MY465, MY457, MY458, and MY459.

\noindent Having taught MY452 and (the old) MY459 this year, I am in a strong position to deliver these courses. The new courses for which I am applying focus on methods that I use extensively in my own research.  In my PhD thesis I focus on the voting and speech-making behaviour of legislators in the European Parliament and the UK House of Commons. I make extensive use of quantitative text analysis methods in the papers in my thesis, as well as situating most of my work within the `potential outcomes' causal inference framework. I therefore feel that I am a suitable candidate to teach on both MY457 and (the new) MY459. I intend to submit my PhD in March 2016.

\noindent As my CV makes clear, I have taken I have taken several courses in quantitative methods here at the LSE as well as in Oxford and, more recently, at Harvard and MIT. I have a strong command of the material of all of the courses mentioned above, and feel that I could deliver clear and engaging classes. 
 
\noindent I would appreciate your consideration of my application for these positions.
 
\closing{Yours sincerely,} 
 

 


\end{letter}
 

\end{document}






